---
title: "AkaikeSummary"
author: "Brian O'Meara"
date: "9/19/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Choosing the correct Akaike penalty term

The AICc is a corrected AIC for small sample size. However, there remains an unaddressed question in phylogenetics regarding what exactly sample size is. For comparative methods, it is taken as number of taxa, as when comparing Ornstein-Uhlenbeck models (Butler and King, 2004; O'Meara et al. 2006; Beaulieu et al. 2012) or discrete character models (corhmm_____). For evaluating molecular models, it is taken as number of sites (Posada _____). These cannot both be true; especially for discrete models, where the underlying model is ultimately the same between DNA and other discrete traits. 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
