---
title: "AkaikeSummary"
author: "Brian O'Meara"
date: "9/19/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Choosing the correct Akaike penalty term

The AICc is a corrected AIC for small sample size; it is supposed to better estimate Kullback-Leibler distance. However, there remains an unaddressed question in phylogenetics regarding what exactly sample size is. For comparative methods, it is taken as number of taxa, as when comparing Ornstein-Uhlenbeck models (Butler and King, 2004; O'Meara et al. 2006; Beaulieu et al. 2012) or discrete character models (corhmm_____). For evaluating molecular models, it is taken as number of sites (Posada _____). These cannot both be true; especially for discrete models, where the underlying model is ultimately the same between DNA and other discrete traits.

Jhwueng et al (____) investigated AIC and related measures of KL distance and found no consistent best option. They used a two stage simulation approach to estimate KL distance. This has since been implemented in the [KLchecker package](https://github.com/bomeara/KLchecker). We used this approach to examine two 

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
